Singapore's Public Housing Affordability

### 2023-11-09 datastory.qmd
Weekly Update

```{r, eval=TRUE,echo=FALSE}
data1999 <- read.csv("docs/src/data/ResaleFlatPrices1999.csv")
data2022 <- read.csv("docs/src/data/ResaleFlatPrices2022.csv")

average_prices_1999 <- data1999 %>%
  group_by(flat_type) %>%
  summarise(Mean1999 = mean(resale_price))

average_prices_2022 <- data2022 %>%
  group_by(flat_type) %>%
  summarise(Mean2022 = mean(resale_price))

@@

ggplot(long_data, aes(x = flat_type, y = AveragePrice, group = Year, color = Year)) +
  geom_line() +
  geom_point() +
  geom_text(aes(label = round(AveragePrice, 2)), hjust = 1, vjust = -1, check_overlap = TRUE, size = 3) +
  scale_y_continuous(labels = label_comma()) + 
  labs(title = "Average Resale Price Each Flat Type in 1999 and 2022 in SG Dollars",
       x = "Flat Type",
       y = "Average Resale Price",
       color = "Year") +
  theme_minimal()

```
<p style="text-align: justify;">
To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg). The publicly available data contains historical sales figures on yearly bases, and can be used to access market dynamics and predict future trend.
</p>

@@

### The Distribution of Resale Flat Prices of Different Flat Types

>>>>

```{r, eval=TRUE,echo=FALSE, fig.align='center'}
data1999 <- read.csv("docs/src/data/ResaleFlatPrices1999.csv")
data2022 <- read.csv("docs/src/data/ResaleFlatPrices2022.csv")

average_prices_1999 <- data1999 %>%
  group_by(flat_type) %>%
  summarise("1999" = mean(resale_price))

average_prices_2022 <- data2022 %>%
  group_by(flat_type) %>%
  summarise("2022" = mean(resale_price))

@@

ggplot(long_data, aes(x = flat_type, y = AveragePrice, group = Year, color = Year)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 3) +
  geom_text(aes(label = sprintf("$%.2f", AveragePrice)), hjust = 1, vjust = -1, check_overlap = TRUE, size = 3) +
  scale_y_continuous(labels = label_comma()) + 
  labs(title = "Average Resale Price in 1999 and 2022 (Flat Type, SGD)",
       x = "Flat Type",
       y = "Average Resale Price",
       color = "Year") +
  theme_minimal()

<p style="text-align: justify;">
To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg). The publicly available data contains historical sales figures on yearly bases, and can be used to access market dynamics and predict future trend. Before moving on to the deeper analysis
</p>

@@

Interactive Bar Graph Placeholder

library(ggplot2)

data <- data.frame(
  category = c("A", "B", "C", "D"),
  value = c(23, 45, 12, 78)
)

ggplot(data, aes(x = category, y = value)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Simple Bar Graph", x = "Category", y = "Value")

```
<p></p>
### The Distribution of Resale Flat Prices of Different Flat Types
